---
title: '`r format(paste(each_journal, "Monthly Report"))`'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
  toc: true
---
<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
         $(document).ready(function() {
             $(".dtable").DataTable();
         } );
</script>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

this_journal <- each_journal #sets the journal for the report

n_stats <- data %>% filter(journal == this_journal) %>% 
  filter(!is.na(measure.values)) %>% nrow()

no_cat_journ <- c("mBio", "MCB") #journals that don't use the category field
```

#Submissions
```{r, journ_subs_plot, fig.width= 8}
source("each_journal_monthly_report/get_journ_subs.R")

sub_trends_plot
```

```{r, journ_subs_cat, fig.asp = .9}
source("each_journal_monthly_report/get_journ_subs.R")

plot_YTD_subs
```

#Transfers
```{r, recent_transfers}
source("each_journal_monthly_report/get_transfers.R")

knitr::kable(J_recent_transfers, format = "html", digits = 2, table.attr = "class='dtable'",  
             col.names = c("Date", "From", "Manuscript Number", "Title", 
                           "Editor", "Decision")) %>%
  add_header_above(header = c("Transfers received in the last month" = 6), 
                   bold = TRUE) %>% 
  kable_styling()

knitr::kable(J_transfers_ytd, 
             format = "html", digits = 2,  table.attr = "class='dtable'", 
             col.names = c("Decision", "N", "Percent")) %>%
  add_header_above(header = c("Final outcomes on transfers recieved in the last 12 months" = 3), bold = TRUE) %>% 
  kable_styling(full_width = TRUE)
```

#Useage Stats
```{r, journ_usage_barplot, fig.width= 8}
if(n_stats != 0){
source("each_journal_monthly_report/get_journ_usage.R")

total_views}
```


```{r}
if(n_stats != 0){date_views}
```


```{r, fig.height=10, fig.width=10}
if(n_stats != 0){cat_views}
```

#10 most-frequently read articles
```{r, top_10_read}
if(n_stats != 0){source("each_journal_monthly_report/get_top_10_read.R")

knitr::kable(top_summary, format = "html", digits = 2,  escape = FALSE, table.attr = "class='dtable'", 
             col.names = c("Editor", "Title", "Publication Date", "Manuscript Type", 
                           "Category", "Total Reads")) %>%
  footnote(general = "Selected from articles published in the last 12 months, ranked on HighWire html & pdf views") %>% 
  kable_styling() %>% 
  scroll_box(width = "100%", height = "300px")}
```

#Citations by category
```{r, journ_cites_category, fig.width= 8}
if(n_stats != 0){source("each_journal_monthly_report/get_journ_cites.R")

total_cites
each_cite}
```

#10 most-frequently cited articles
```{r, top_10_cited}
if(n_stats != 0){source("each_journal_monthly_report/get_top_10_cited.R")

knitr::kable(top_cited_summary, format = "html", table.attr = "class='dtable'", 
             digits = 2,  escape = FALSE,
             col.names = c("Editor", "Title", "Publication Date", "Manuscript Type", "Category", "Total Cites")) %>%
  footnote(general = "Selected from articles published in the previous 12 - 36 months") %>% 
  kable_styling() %>% 
  scroll_box(width = "100%", height = "300px")}
```


#Acceptance and rejection rates by article type
```{r, editor_manu_type}
source("each_journal_monthly_report/get_editor_manu_type.R")

knitr::kable(article_summary, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2,    
             col.names = c("Manuscript Type", "Decision", "N", "%")) %>%  
  collapse_rows() %>% 
  footnote(general = "Includes all submissions YTD") %>% 
  kable_styling()
```


#Number of original manuscripts assigned to editors
```{r editor_assign}
source("each_journal_monthly_report/get_editor_assign.R") 

knitr::kable(editor_assign_all_summary, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2) %>% 
  footnote(general = "Manuscripts assigned to each editor for the YTD") %>% 
  kable_styling()
```

#Days to first decision by editor
```{r, editor_dec}
source("each_journal_monthly_report/get_editor_desc_days.R") 

knitr::kable(editor_desc_year_sums, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2,  
             col.names = c("Editor", "N", "Average", "Median", "Minimum", "Maximum")) %>%
  footnote(general = "Includes decisions made following peer review on initial submissions in the last 12 months") %>% 
  kable_styling()
```


#Acceptance and rejection rates by editor
```{r, editor_acc_rej}
source("each_journal_monthly_report/get_editor_acc_rej_rates.R") 

knitr::kable(editor_acc_rej_summary, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2,  
             col.names = c("Editor", "N", "%", "N", "%", "N", "%")) %>% 
  add_header_above(c(" ", "Editorial Rejections" = 2, "Rejected" = 2, "Accepted" = 2)) %>% 
  footnote(general = "Includes all decisions made in the last 12 months") %>% 
  kable_styling()
```


#Problem manuscript report
```{r, problem_manus}
source("each_journal_monthly_report/get_problem_manus.R")

knitr::kable(problem_data, format = "html", digits = 2, table.attr = "class='dtable'",   
             col.names = c("Manuscript Number", "Editor", "Recieved Date", "Decision Date", "Days Since Decision", "Status")) %>%
  kable_styling()
```

