---
title: "ASM All Journals Monthly Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    df_print: paged
---
<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
         $(document).ready(function() {
             $("table").DataTable();
         } );
</script>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

#Submissions
```{r, asm_subs_plot, results='asis'}
source("monthly_report/plot_asm_subs.R")

asm_subs_plot
```

#Submissions YTD
```{r, subs_table}
source("monthly_report/get_subs.R")

knitr::kable(sum_month, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2) %>% 
  footnote(general = "Submissions recieved by each journal for this calendar year") %>% 
  kable_styling()
```

#Time to first decision or publication 
```{r, time_to_desc, results='asis'}
source("monthly_report/get_day_stats.R")

knitr::kable(day_summary, format = "html", digits = 2, col.names = c("Journal", "N", "Avg", "Med", "N", "Avg")) %>%
  add_header_above(c(" ", "Days to First Decision" = 3, "Days to Publication" = 2)) %>% 
  footnote(general = "Data presented in days, and includes all manuscripts submitted and reviewed in the last 12 months (does not include editorial rejections)") %>% 
  kable_styling()
```

#Acceptance & rejection rates 
```{r, acc_rej_rates, results='asis'}
source("monthly_report/get_acc_rej_rates.R")

knitr::kable(acc_rej_summary, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2,  
             col.names = c("Journal", "N", "%", "N", "%", "N", "%")) %>%
  add_header_above(c(" ", "Editorial Rejections" = 2, "Rejections" = 2, "Accepted" = 2)) %>% 
  footnote(general = "Includes all manuscripts with a decision made in the last 12 months") %>% 
  kable_styling()
```

#Transfers YTD
```{r, transfers}
source("monthly_report/get_transfer_journals.R")
plot_trans

knitr::kable(all_transfers_ytd, format = "html", digits = 2, 
             col.names = c("Decision", "N", "%")) %>%
  footnote(general = "Includes all manuscripts transfered in this calendar year") %>% 
  kable_styling()
```

#Useage Stats of Articles Published in Last 12 Months
```{r, journ_usage_barplot}
source("monthly_report/get_journ_usage_barplot.R")

abstract_plot
html_plot
pdf_plot
```


```{r, asm_usage_overtime, fig.height = 10, fig.width= 8}
source("monthly_report/get_asm_usage_overtime.R")

asm_time
pdf_cat
html_cat
abstract_cat
```


#Total Cites for Articles Published in Previous 12 - 36 Months
```{r, asm_cites_journ, fig.height = 6, fig.width= 8}
source("monthly_report/get_asm_cites_journ.R")

journal_cites_plot
cat_cites_plot
```

#Estimated Journal Impact Factors
```{r, est_jifs}
source("monthly_report/get_est_jif.R")

knitr::kable(est_jif, format = "html", 
             table.attr = "class='dtable'", escape = FALSE, digits = 2,
             col.names = c("Journal", "Total Cites", 
                                                                 "Citable Items", "Impact Factor")) %>%
  footnote(general = "Rolling impact factor calculated from citations over the last 12-24 months on 
           publications 24 to 48 months old") %>% 
  kable_styling()